%
% Unless otherwise indicated, the copyright in this material is 
% owned by Joerg Evermann. This material is licensed to you under the 
% Creative Commons by-attribution non-commercial license (CC BY-NC 4.0)}
%

Dr. Joerg Evermann is an associate professor at the Faculty of Business Administration at Memorial University of Newfoundland. He received his PhD in Information Systems in 2003 from the University of British Columbia. Prior to joining Memorial University in 2007, Dr. Evermann was a lecturer in Information Systems with the School of Information Management at the University of Wellington, New Zealand. 

Dr. Evermann's interests are in business process management, statistical methods, and information integration. Dr. Evermann has published his research in more than 80 peer-reviewed publications. His work has appeared in high-quality journals, such as European Journal of Marketing, Decision Support Systems, IEEE Transactions on Software Engineering, IEEE Transactions on Knowledge and Data Engineering, IEEE Transactions on Services Computing, Journal of Business Research, Organizational Research Methods, Structural Equation Modeling, Journal of the AIS, Information systems, and Information Systems Journal. Dr. Evermann has presented his work at international conferences, such as ICIS, AMCIS, CAiSE, ER, among others. He is an associate editor for the Communications of the AIS (CAIS) and the Business Information Systems Engineering (BISE) journals and serves regularly on the program committee of the BPM, ICPM, CBI and AI4BPM conferences and workshops.

